Won’t you be my neighboR?

### 2019-05-20 msu-workshop-2019.Rmd
update

---
title: "Won’t you be my neighboR?"
subtitle: "An introduction to R for data science in education"
author: "Joshua Rosenberg and Emily Bovee"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

"Packages" are shareable collections of R code that provide functions (i.e., a command to perform a specific task), data and documentation,. Packages increase the functionality of R by improving and expanding on base R (basic R functions).

@@

d1 %>% 
  mutate(var2 = ifelse(vec1 >= .5, "greater", "lesser"))
```

@@

```{r}
d1 %>% 
  mutate(var2 = case_when(
    var1 >= .75 ~ "a lot",
    var1 >= .5 ~ "greater",
    var1 < .5 ~ "lesser",
    var1 <= .25 ~ "very little" 
  ))
```

@@

2. We concatenate the working directory file path to the desired file name for the CSV using a *function* called `paste0`. This is stored in another *object* called `student_reponses_file_name`. This creates a file name with a *file path* in your working directory and it saves the file in the folder that you are working in.

@@

@@

```{r, warning = FALSE, out.width = "450px", fig.align = "center"}
ggplot(student_mot_vars,
       aes(x = student_efficacy, y = student_broad_interest)) +
  geom_point() +
  geom_smooth(method = "lm")
```

# Scatter plot with a regression line and some cleaning up

```{r, warning = FALSE, out.width = "450px", fig.align = "center"}
ggplot(student_mot_vars,
       aes(x = student_efficacy, y = student_broad_interest)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  xlab("Student Efficacy") +
  ylab("Student Broad Interest")
```

@@

@@

>>>>

---
title: "Won’t you be my neighboR?"
subtitle: "An introduction to R for data science in education"
author: "Joshua Rosenberg and Emily Bovee"
date: "2018-05-16"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

"Packages" are shareable collections of R code that provide functions (i.e., a command to perform a specific task), data, and documentation. Packages increase the functionality of R by improving and expanding on base R (basic R functions).

@@

d1 %>% 
  mutate(var2 = ifelse(var1 >= .5, "greater", "lesser"))
```

@@

```{r}
d1 %>% 
  mutate(var2 = case_when(
    var1 >= .75 ~ "a lot",
    var1 >= .5 & var1 < .75 ~ "greater",
    var1 >= .25 & var1 < .5  ~ "lesser",
    var1 < .25 ~ "very little" 
  ))
```

@@

2. We concatenate the working directory file path to the desired file name for the CSV using a *function* called `str_c`. This is stored in another *object* called `student_reponses_file_name`. This creates a file name with a *file path* in your working directory and it saves the file in the folder that you are working in.

@@

*The doc is [here](https://github.com/jrosen48/MSU-workshop-2019/blob/master/demo-doc.Rmd) in the repository*

@@

```{r, warning = FALSE, out.width = "350px", fig.align = "center"}
ggplot(student_mot_vars,
       aes(x = student_efficacy, y = student_broad_interest)) +
  geom_point() +
  geom_smooth(method = "lm")
```
---
# Cleaning up

```{r, warning = FALSE, out.width = "350px", fig.align = "center"}
ggplot(student_mot_vars,
       aes(x = student_efficacy, y = student_broad_interest)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  xlab("Student Efficacy") +
  ylab("Student Broad Interest")
```
---

@@

*The doc is [here](https://github.com/jrosen48/MSU-workshop-2019/blob/master/demo-doc.Rmd) in the repository*
---

@@

# Contact

- [Joshua Rosenberg](mailto:jmrosenberg@utk.edu)
- [Emily Bovee](mailto:emily.a.bovee@gmail.com)
